SDR enhancement by clouds

### 2024-04-02 article/article.tex
Commit 2024-04-02 11:11

\title{SDR enhancement by clouds}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A Short Subtitle}
\author{Athanasios N. Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
\date{2024-04-01}

@@

@@

Some of the proposed underling mechanisms of those events have been summarized
by Gueymard (2017), and include scattering on the edge of cumulus clouds or through
thin cirrus. Further investigation with radiation transfer modeling methods and
observations have pointed as the prevailing mechanism, the forward Mie scattering
(Pecenak et al. 2016; Thuillier et al. 2013; G. H. Yordanov et al. 2013; Georgi Hristov Yordanov, Saetre, and Midtgård 2015), through the clouds.
The overall phenomenon depends on different interactive factors, that include cloud
thickness and constitution, and the relative position of the sun, the clouds, and the
observer. As such, there multiple contributing mechanism can create the
observed irradiance enhancements.

@@

Study of the mechanism has also been done with modeling of different cloud types and
atmospheric conditions.
Gueymard (2017); Veerman, Van Stratum, and Van Heerwaarden (2022)

>>>>

\title{SDR enhancement by clouds}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A Short Subtitle}
\author{Athanasios N. Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
\date{2024-04-02}

@@

Some of the proposed underling mechanisms of those events have been summarized by
Gueymard (2017), and include scattering on the edge of cumulus clouds or through thin
cirrus. Further investigation with radiation transfer modeling methods and
observations have pointed as the prevailing mechanism, the forward Mie scattering
(Pecenak et al. 2016; Thuillier et al. 2013; G. H. Yordanov et al. 2013; Georgi Hristov Yordanov, Saetre, and Midtgård 2015), through the clouds.
The overall phenomenon depends on different interactive factors, that include cloud
thickness, constitution and type, and the relative position of the sun, the clouds,
and the observer (Gueymard 2017; Veerman, Van Stratum, and Van Heerwaarden 2022). As such, there are multiple contributing mechanism that can create
the observed irradiance enhancements.

@@

@@
